
## Introduction to the Tidyverse_Datacamp

Description:

- Focused on a powerful set of tools, Tidyverse.
- Learn the intertwined processes of data manipulation and visualization using the tools dplyr and ggplot2. 
- Learn to manipulate data by filtering, sorting, and summarizing a real dataset of historical country data in order to answer exploratory questions. 
- Learn to turn this processed data into informative line plots, bar plots, histograms, and more with the ggplot2 package.

### 1. Data wrangling


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(dplyr)
library(knitr)
```

#### a. Filtering in R
**Dataset gapminder**

```{r echo = FALSE, results='asis'}
kable(gapminder[1:5,])
```

**Filtering 1 year**
```{r echo = FALSE, results='asis'}
kable(head(gapminder %>%
  filter(year == 1957),5))
```

**Filtering for one country and one year**

```{r echo = FALSE, results='asis'}
kable(head(gapminder %>%
  filter(country == "China", year == 2002),5))
```

Sort in ascending order of lifeExp

```{r echo=FALSE, results='asis'}

# Sort in ascending order of lifeExp
kable(head(gapminder %>%
arrange(lifeExp),5))
```

Sort in descending order of lifeExp

```{r echo=FALSE, results='asis'}  
kable(head(gapminder %>%
arrange(desc(lifeExp)),5))
```

Filter for the year 1957, then arrange in descending order of population

```{r echo=FALSE, results='asis'} 
kable(head(gapminder %>%
  filter(year == 1957) %>%
  arrange(desc(pop)),5))
```

Use mutate to create a new column called lifeExpMonths

```{r echo = FALSE, results= 'asis'}
kable(head(gapminder %>%
  mutate(lifeExpMonths = 12*lifeExp),5))
```

# Filter, mutate, and arrange the gapminder dataset

```{r echo = FALSE, results='asis'}
kable(head(gapminder %>%
  filter(year == 2007) %>%
  mutate(lifeExpMonths =12*lifeExp) %>%
  arrange(desc(lifeExpMonths)),5))

```








